Analyzing the Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-10-19 FirstDraftRMarkdown.Rmd
Add files via upload

# V. Discussion 
|	We definitely see an impact of playing the 2020 NBA playoffs in the bubble, there were some minor surprises in the results of the study, but overall it seemed that away teams fared better in the bubble than previous years. Starting from the dip in home winning percentage to below .482 it’s clear something was different. Although the results were not significant after a Bonferonni correction it’s still important to consider and understand that home teams seemed to struggle to win compared to normal conditions.  
|	Moving on to total scoring. As previously stated, this is perhaps the most important measure of a basketball game given that it is what ultimately decides the winner. So these conclusions are particularly interesting and valuable. While the home teams in 2020 did see a slight uptick in average scoring it was not large enough to be statistically significant. However, away team average scoring did increase by a statistically significant amount. This goes hand in hand with our intuition and conclusion about the home winning percentage decreasing. If away teams are scoring significantly more and home teams are not, then we expect to see away teams winning a larger amount of games. This may give a little more reason to believe the conclusion that there was a significant decrease in home winning percentage, despite failing to be significant after Bonferroni correction.  Also, these conclusions give reason to believe that home-court advantage stems mainly from adverse effects on the visiting team.  
|  So away teams are scoring more points, where are those points coming from? The initial thought should be shooting percentage. It seems pretty obvious if you shoot better from the field you are going to score more points. Here we found that away teams are shooting significantly better from two-point shots. However, we know the three point shooting and free-throw shooting were not significantly different. Also, it is important to remember that there’s other factors besides scoring that may affect outcome of games, but were not considered in this study. Another future study may want to look into other potential factors to help understand and expand on how away teams improved.  
|  Surprisingly, it appeared for the most part that home team performance was unaffected by playing in the bubble. They saw some slight insignificant increases in total scoring, two point shooting, three point shooting and free throw shooting. The home teams did not appear to perform any differently, in terms of scoring and scoring efficiency, while playing on a neutral court.  
|  Overall, it appears that away teams were able to close the gap with home teams with home-court advantage removed. Away teams significantly increased their scoring, partly due to the fact of increased two point shooting efficiency. However, there are other potential sources of added scoring worth researching. For example, turnovers, steals, assist, rebounds, and many more game statistics. There are plenty of other possibilities besides just shooting efficiency to pick through looking for more possible sources of added points for away teams. Ultimately, home teams were not largely impacted in terms of their overall performance. It seems their failure to win in 2020, is more due to better away performance than any decrease in their own performance. In fact, the only significant change for home teams found in this study was actually an improvement.

>>>>

# V. Discussion 
|	We definitely see an impact of playing the 2020 NBA playoffs in the bubble, there were some minor surprises in the results of the study, but overall it seemed that away teams fared better in the bubble than previous years. Starting from the dip in home winning percentage to below .482 it’s clear something was different. Although the results were not significant after a Bonferroni correction it’s still important to consider and understand that home teams seemed to struggle to win compared to normal conditions.  
|	Moving on to total scoring. As previously stated, this is perhaps the most important measure of a basketball game given that it is what ultimately decides the winner. So these conclusions are particularly interesting and valuable. While the home teams in 2020 did see a slight uptick in average scoring it was not large enough to be statistically significant. However, away team average scoring did increase by a statistically significant amount. This goes hand in hand with our intuition and conclusion about the home winning percentage decreasing. If away teams are scoring significantly more and home teams are not, then we expect to see away teams winning a larger amount of games. This may give a little more reason to believe the conclusion that there was a significant decrease in home winning percentage, despite failing to be significant after Bonferroni correction.  Also, these conclusions give reason to believe that home-court advantage stems mainly from adverse effects on the visiting team.  
|  So away teams are scoring more points, where are those points coming from? The initial thought should be shooting percentage. It seems pretty obvious if you shoot better from the field you are going to score more points. Here we found that away teams are shooting significantly better from two-point shots. However, we know the three point shooting and free-throw shooting were not significantly different. Also, it is important to remember that there’s other factors besides scoring that may affect outcome of games, but were not considered in this study. Another future study may want to look into other potential factors to help understand and expand on how away teams improved.  
|  Surprisingly, it appeared for the most part that home team performance was unaffected by playing in the bubble. They saw some slight insignificant increases in total scoring, two point shooting, three point shooting and free throw shooting. The home teams did not appear to perform any differently, in terms of scoring and scoring efficiency, while playing on a neutral court.  
|  Overall, it appears that away teams were able to close the gap with home teams with home-court advantage removed. Away teams significantly increased their scoring, partly due to the fact of increased two point shooting efficiency. However, there are other potential sources of added scoring worth researching. For example, turnovers, steals, assist, rebounds, and many more game statistics. There are plenty of other possibilities besides just shooting efficiency to pick through looking for more possible sources of added points for away teams. Ultimately, home teams were not largely impacted in terms of their overall performance. It seems their failure to win in 2020, is more due to better away performance than any decrease in their own performance. In fact, the only significant change for home teams found in this study was actually an improvement.
